Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 algorithm_regret.tex
addressed Peter's comments

\dkedit{
For most of the proof, we will focus on the case $g(s) \leq \TieCutoff$.
The remaining phases are the ones with
$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 \TieCutoff^2$.}
\pfcomment{Is there a typo in the previous line?  Shouldn't it be 
$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 / \TieCutoff^2$?
Or am I missing something?}
\dkedit{Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
in expectation by Lemma~\ref{lem:phase-length},
and each step incurs regret at most \MAXR.
The total expected regret incurred in these phases is at most
$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3 \TieCutoff^3$.}

>>>>

\dkedit{
For most of the proof, we will focus on the case $g(s) \leq \TieCutoff$.
The remaining phases are the ones with
$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.}
\dkedit{Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
in expectation by Lemma~\ref{lem:phase-length},
and each step incurs regret at most \MAXR.
The total expected regret incurred in these phases is at most
$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3$.}
